The rest of the thesis is structured as follows:
	
\begin{description}
	\item[Chapter \ref{chapter:3d_ultrasonography}] introduces the field of 3D ultrasonography. Methods of reconstructing a volume from ultrasound scans and techniques to visualize the volume are described. Previous work in the field of ultrasound reconstruction and visualization is also presented.
	\item[Chapter \ref{chapter:gpgpu}] introduces general purpose computations on GPUs (GPGPU). A brief history and current state of GPU computing is presented, and the recent OpenCL architecture for GPGPU is described.
	\item[Chapter \ref{chapter:gpu_reconstruction}] describes the approach developed in this thesis where the GPU is utilized to perform fast reconstruction of ultrasound scans acquired in beforehand.
	\item[Chapter \ref{chapter:incremental_reconstruction_visualization}] describes the approach developed in this thesis for real-time incremental reconstruction and volume visualization performed on the GPU simultaneously as the data is acquired.
	\item[Chapter \ref{chapter:results_discussion}] presents the performance and quality of the ultrasound reconstruction and visualization as performed in this thesis. These results are also discussed together with other important issues.
	\item[Chapter \ref{chapter:conclusion_future_work}] summarizes the findings of the work described in this thesis and presents possible avenues of future work.
	\item[Appendix \ref{chapter:annotated_bib}] contains an annotated bibliography of selected references.
	\item[Appendix \ref{chapter:large_figures}] contains large uncropped versions of selected figures.
	\item[Appendix \ref{chapter:poster}] contains a poster summarizing the principles and main results of this thesis with focus on the incremental reconstruction.
	\item[Appendix \ref{chapter:test_measurements}] contains additional numerical test measurements.
	\item[Appendix \ref{chapter:optix_paper}] contains a paper about ray tracing on the GPU using the Nvidia OptiX library, including volume ray casting.
	\item[Appendix \ref{chapter:code_listings}] contains selected code listings from implementations of the methods described in this thesis.
	
\end{description}